---
title: Georgia Strait Air Zone
header-includes:
- \usepackage{booktabs}
- \usepackage{makecell}
- \usepackage{multirow}
- \usepackage{colortbl}
- \usepackage{xcolor}
output:
  pdf_document:
    latex_engine: lualatex
mainfont: Arial
params:
  ozone: !r ozone_caaqs_results
  annual_ozone: !r ozone_caaqs$ann_4th_highest
  pm25: !r pm_caaqs_combined_results
  pm25_24h: !r pm_24h_caaqs_results
  annual_pm25: !r pm25_caaqs_annual$yearly_avg
  stations: !r stations_az
  airzone: "Georgia Strait"
---

```{r setup, echo = FALSE, message = FALSE}
## Source plotting and table functions. Also loads packages.
source("functions.R")

## Filter data to air zone
airzone <- params$airzone
ozone <- filter(params$ozone, airzone == !!airzone)
pm25 <- filter(params$pm25, airzone == !!airzone)
```

## Fig 2: 3 year ozone concentration by station

```{r ozone-by-station, echo = FALSE, warn = FALSE}
plot_ozone_by_station(ozone, airzone)
```

## Fig 3: Annual trends in ozone concentrations (2007-2016), based on annual 4th highest daily 8-hour maxima for a single year.

```{r annual-ozone, echo = FALSE, warning = FALSE}
## Add station names
annual_ozone <- params$annual_ozone %>%
  left_join(params$stations, by = c("ems_id", "station_name")) %>%
  filter(airzone == !!airzone)

plot_ozone_station_timeseries(annual_ozone, airzone)
```

## Fig 4: PM 2.5 by station

```{r pm25-by-station, echo = FALSE, warning = FALSE, fig.asp = 1.3}
plot_pm25_by_station(pm25)
```

## Fig 5: PM Annual trends in PM 2.5

```{r annual-pm25, echo = FALSE, warning = FALSE}
## Add station names
annual_pm25 <- params$annual_pm25 %>%
  left_join(params$stations, by = c("ems_id", "station_name")) %>%
  filter(airzone == !!airzone)  

plot_pm25_station_timeseries(annual_pm25, airzone)
```

## Table 2:  Summary of ozone concentrations as measured and air zone management levels for the `r airzone` Air Zone

```{r table-2, echo = FALSE}
create_ozone_table(ozone)
```

## Table 3: Summary of PM2.5 concentrations as measured and air zone management levels for the `r airzone` Air Zone

```{r table-3, echo = FALSE}
params$pm25_24h %>%
  filter(airzone == !!airzone) %>%
  create_pm25_table()
```
