## Air Zone Management Levels

```{r calculations for air zone mangement}

mgmt_colours <- rcaaqs::management_levels %>% 
  select(mgmt_level = labels, mgmt_col = colour_text) %>% 
  distinct()

# calculate ozone management level 
oz_man <- ifelse(max(ozone$metric_value_ambient, na.rm = TRUE) == 
                   max(ozone$metric_value_mgmt, na.rm = TRUE), "did not", "did")

oz_col <- mgmt_colours$mgmt_col[mgmt_colours$mgmt_level == o3_az$mgmt_level]

pm24_man_impact <- ifelse(
  pm24$metric_value_ambient == pm24$metric_value_mgmt, "did not", "did"
)

pm_annual_man_impact <- ifelse(
  pm_annual$metric_value_ambient == pm_annual$metric_value_mgmt, "did not", "did"
)

pm_col <- mgmt_colours$mgmt_col[mgmt_colours$mgmt_level == pm25_mgmt$mgmt_level]
```


Air zone management levels are assigned on the basis of the highest concentrations within an air zone, excluding contributions from transboundary flows (TF) and exceptional events (EE) such as wildfires. This is done so that long-term management strategies are not developed on the basis of events that are beyond local or provincial control. 

In the `r airzone` Air Zone, wildfires are the primary contributor to TF/EE. The methodology for identifying wildfire-influenced data is provided in Appendix I. 

Table 2 summarizes ozone concentrations as measured before and after consideration of any TF/EE influences. TF/EE influences `r oz_man` affect management levels. Consequently, the `r airzone`  Air Zone is assigned a `r oz_col `  management level, based on ozone levels in Fort St. John. This indicates that any ozone-related actions should focus on `r as.character(o3_az$mgmt_level)`.

Table 3 summarizes both as-measured PM~2.5~ concentrations and management levels once estimated wildfire influences have been removed. As discussed further in Appendix II, wildfire influences were identified, but the impact on management levels was small. The air zone is assigned a `r pm_col` management level for PM~2.5~. This means that PM~2.5~-related actions should focus on `r pm25_mgmt$mgmt_level`.

<!-- Summary of ozone concentrations as measured and air zone management levels -->

```{r table-2}
create_ozone_table(ozone, airzone)
```

<!-- Summary of PM2.5 concentrations as measured and air zone management levels -->

```{r table-3}
create_pm25_table(pm25, airzone)
```

## Actions to Protect Air Quality

Air quality activities in the `r airzone` Air Zone have largely focused on characterizing air quality in this region and identifying potential impacts from the oil and gas sector. As part of the `r airzone` Air Quality Monitoring Project, surveillance monitoring was conducted in a number of smaller communities that are closer to oil and gas production. An analysis of this monitoring data is summarized in the "Northeast Air Quality Monitoring Report" (see: <https://www2.gov.bc.ca/assets/gov/environment/air-land-water/air/reports-pub/northeast_bc_air_quality_assessment_report.pdf>). 

A description of other activities underway in B.C. air zones can be found in the "Air Zone Management Response for British Columbia" (see:<https://www2.gov.bc.ca/gov/content/environment/air-land-water/air>). 
