```{r,echo=FALSE,message=FALSE,warning=FALSE,results='hide'}
airzone <- 'Central Interior'
year <- 2021


library(kableExtra)
library(readr)

source('00_setupmonitors.R')
# setwd('../../../../')
aqhi_stations   #retrieved from above
stations <- stations %>%
  mutate(Operator = recode(OWNER,
                           'MVRD' ='Metro Vancouver',
                           'ENV'='ENV',
                           'INDUSTRY' = 'Industry'))

aqhi_stations_airzone <- aqhi_stations %>%
  rename(AIRZONE = airzone) %>%
  filter(AIRZONE %in% airzone)

stations_airzone <- stations %>%
  filter(AIRZONE %in% airzone) %>%
  select(Label,Operator,monitors,OWNER) %>%
  
  distinct()

station_env <- stations_airzone %>%
  filter(OWNER == 'ENV') %>%
  nrow()
station_industry <- stations_airzone %>%
  filter(OWNER == 'INDUSTRY') %>%
  nrow()

station_count <-
  stations_airzone %>%
  mutate(txt_owner = recode(OWNER,
                            'ENV'='the Ministry of Environment and Climate Change Strategy (ENV)',
                            'INDUSTRY'='Industry')) %>%
  group_by(txt_owner) %>%
  summarise(count=n()) %>%
  mutate(txt = paste(txt_owner,' (',count,' stations)',sep=''))

txt <- to_comma_string(station_count$txt)
```

## Monitoring in the `r airzone` Air Zone

There are `r nrow(stations_airzone)` air quality monitoring stations in the `r airzone` Air Zone that were active from `r year-2` to `r year`. These stations were operated by `r txt`. 

```{r,echo=FALSE,warning=FALSE,message=FALSE}
stations_airzone %>%
  select(Label,Operator,monitors) %>%
  arrange(Label) %>% distinct() %>%
  rename(Station = Label,
         Monitors = monitors) %>%
  kable("html",escape = FALSE) %>%
  kable_styling() 
```



The `r airzone` has `r nrow(aqhi_stations_airzone)` locations where the Air Quality Health Index (AQHI) are reported. AQHI is a communication tool used to report the health impacts of poor air quality. It is calculated from the measured levels of fine particulate matter(PM<sub>2.5</sub>), ground-level ozone(O<sub>3</sub>), and nitrogen dioxide(NO<sub>2</sub>). 

```{r,echo=FALSE,warning=FALSE,message=FALSE}
aqhi_stations_airzone %>%
  dplyr::rename(`AQHI Locations` = AQHI_AREA) %>%
  select(`AQHI Locations`)%>%
  kable("html") %>%
  kable_styling() 
```
