```{r,echo=FALSE,message=FALSE,warning=FALSE,results='hide'}
airzone <- 'Central Interior'
year <- 2021


library(kableExtra)
library(readr)

source('00_setupmonitors.R')
# setwd('../../../../')
aqhi_stations   #retrieved from above
stations <- stations %>%
  mutate(Operator = recode(OWNER,
                           'MVRD' ='Metro Vancouver',
                           'ENV'='ENV',
                           'INDUSTRY' = 'Industry'))

  aqhi_stations_airzone <- aqhi_stations %>%
    rename(AIRZONE = airzone) %>%
    filter(AIRZONE %in% airzone)

stations_airzone <- stations %>%
  filter(AIRZONE %in% airzone) %>%
  select(Label,Operator,monitors,OWNER) %>%
  
  distinct()

station_env <- stations_airzone %>%
  filter(OWNER == 'ENV') %>%
  nrow()
station_industry <- stations_airzone %>%
  filter(OWNER == 'INDUSTRY') %>%
  nrow()

station_count <-
stations_airzone %>%
  mutate(txt_owner = recode(OWNER,
                            'ENV'='the Ministry of Environment and Climate Change Strategy (ENV)',
                            'INDUSTRY'='Industry')) %>%
  group_by(txt_owner) %>%
  summarise(count=n()) %>%
  mutate(txt = paste(txt_owner,' (',count,' stations)',sep=''))

txt <- to_comma_string(station_count$txt)
```

## Monitoring in the `r airzone` Air Zone

There are `r nrow(stations_airzone)` air quality monitoring stations in the `r airzone` Air Zone that were active from `r year-2` to `r year`. These stations were operated by `r txt`. Data from ENV and industry monitoring stations that are regulated by the province are validated at regular intervals by the Ministry air data validation team. The monitoring stations and equipment are also audited twice a year by the Ministry audit team.

```{r,echo=FALSE,warning=FALSE,message=FALSE}
stations_airzone %>%
  select(Label,Operator,monitors) %>%
  arrange(Label) %>% distinct() %>%
  rename(Station = Label,
         Monitors = monitors) %>%
  kable("html",escape = FALSE) %>%
  kable_styling() 
```



The `r airzone` also have `r nrow(aqhi_stations_airzone)` Air Quality Health Index (AQHI) locations. AQHI is a communication tool used to report the health impacts of poor air quality. It is calculated from the measured levels of fine particulate matter(PM<sub>2.5</sub>), ground-level ozone(O<sub>3</sub>), and nitrogen dioxide(NO<sub>2</sub>). 

```{r,echo=FALSE,warning=FALSE,message=FALSE}
aqhi_stations_airzone %>%
  dplyr::rename(Location = AQHI_AREA) %>%
  select(Location)%>%
  kable("html") %>%
  kable_styling() 
```
