```{r,echo=FALSE,message=FALSE,warning=FALSE,results='hide'}
airzone <- 'Central Interior'



library(kableExtra)
library(readr)

source('00_setupmonitors.R')
# setwd('../../../../')
aqhi_stations   #retrieved from above
stations

  aqhi_stations_airzone <- aqhi_stations %>%
    rename(AIRZONE = airzone) %>%
    filter(AIRZONE %in% airzone)

stations_airzone <- stations %>%
  filter(AIRZONE %in% airzone) %>%
  distinct()

station_env <- stations_airzone %>%
  filter(OWNER == 'ENV') %>%
  nrow()
station_env <- stations_airzone %>%
  filter(OWNER == 'INDUSTRY') %>%
  nrow()
```

## Monitoring in the `r airzone` Air Zone

There are `r nrow(stations_airzone)` monitoring stations in the `r airzone` Air Zone. There are `r nrow(aqhi_stations_airzone)` Air Quality Health Index (AQHI) locations in the air zone. AQHI is a communication tool used to report the health impacts of poor air quality. It is calculated from the measured levels of fine particulate matter(PM<sub>2.5</sub>), ground-level ozone(O<sub>3</sub>), and nitrogen dioxide(NO<sub>2</sub>). 

```{r}
stations %>%
  select()
```
