## Central Interior Air Zone

The Central Interior air zone is one of seven broad air zones in British Columbia. It covers the Omineca Region, the Cariboo Region, and parts of the Skeena Region. This air zone includes population centres like Smithers, Prince George, Quesnel, and Williams Lake. Air quality monitoring within the Central Interior air zone includes stations operated by the Ministry, community airshed management roundtables, and industrial permits. These stations are strategically located to measure population exposure near major urban centres or determine the impact of industrial emissions. In recent years, this air zone has experienced significant air quality events due to the increasing frequency and intensity of wildfires.

#### Major Municipalities

The top five most populous cities/towns in the Central Interior Air Zone are:

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
library(dplyr)
library(kableExtra)
df_cities <- readr::read_csv('https://raw.githubusercontent.com/bcgov/air-zone-reports/master/data/out/cities.csv')

tbl_cities <- df_cities %>%
  filter(airzone == 'Central Interior')  %>%
  select(Name,C1_COUNT_TOTAL) %>%
   mutate(C1_COUNT_TOTAL = format(C1_COUNT_TOTAL,big.mark = ',')) %>%
  rename(Municipality = Name, `Population (2021)` = C1_COUNT_TOTAL) %>%
  arrange(desc(`Population (2021)`)) %>%
  ungroup() %>%
  dplyr::slice_head(n=5)
```

```{r, echo = FALSE}

kable(tbl_cities)%>%
 kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
