## Coastal Air Zone

The Coastal air zone is one of the seven air zones in British Columbia. It covers the coastal areas of B.C. outside of the Georgia Basin, including Haida Gwaii, the north and central coasts, and northern Vancouver Island. Air quality monitoring in the Coastal air zone includes a station operated by the Ministry of Environment and Climate Change Strategy in Terrace, a station operated by the Prince Rupert Port Authority in Prince Rupert, and several monitoring stations operated by the Kitimat Airshed Group and industry in Kitimat. 

#### Major Municipalities

The top five most populous cities/towns in the Coastal Air Zone are:

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
library(dplyr)
library(kableExtra)
df_cities <- readr::read_csv('https://raw.githubusercontent.com/bcgov/air-zone-reports/master/data/out/cities.csv')

tbl_cities <- df_cities %>%
  filter(airzone == 'Coastal')  %>%
  select(Name,C1_COUNT_TOTAL) %>%
   mutate(C1_COUNT_TOTAL = format(C1_COUNT_TOTAL,big.mark = ',')) %>%
  rename(Municipality = Name, `Population (2021)` = C1_COUNT_TOTAL) %>%
  arrange(desc(`Population (2021)`)) %>%
  ungroup() %>%
  dplyr::slice_head(n=5)

nrow(tbl_cities)
```

```{r, echo = FALSE}

kable(tbl_cities)%>%
 kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
