## Georgia Strait Air Zone

The Georgia Strait air zone is one of the seven broad air zones in British Columbia. It covers the coastal areas of southwestern B.C. outside of the Lower Fraser Valley, and includes municipalities in the Capital Regional District, Cowichan Valley Regional District, Comox Valley Regional District, Alberni-Clayoquote Regional District, Nanaimo Regional District, qathet Regional District, Squamish-Lillooet Regional District, Strathcona Regional District, Sunshine Coast Regional District, and all the Gulf Islands.

#### Major Municipalities

The top five most populous cities/towns in the Georgia Strait Air Zone are:

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
library(dplyr)
library(kableExtra)
df_cities <- readr::read_csv('https://raw.githubusercontent.com/bcgov/air-zone-reports/master/data/out/cities.csv')

tbl_cities <- df_cities %>%
  filter(airzone == 'Georgia Strait')  %>%
  select(Name,C1_COUNT_TOTAL) %>%
   mutate(C1_COUNT_TOTAL = format(C1_COUNT_TOTAL,big.mark = ',')) %>%
  rename(Municipality = Name, `Population (2021)` = C1_COUNT_TOTAL) %>%
  arrange(desc(`Population (2021)`)) %>%
  ungroup() %>%
  dplyr::slice_head(n=5)

nrow(tbl_cities)
```
```{r, echo = FALSE}

kable(tbl_cities)%>%
 kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
