## Lower Fraser Valley Air Zone

The Lower Fraser Valley (LFV) air zone is one of the seven air zones in British Columbia. It is located in southwestern B.C., along the coast and the border with Washington State. Within the LFV air zone are the Metro Vancouver Regional District (MVRD) and the Fraser Valley Regional District (FVRD). The MVRD represents the largest and most densely populated metropolitan area in B.C. It has delegated authority, under the Environmental Management Act, to manage air pollution and air quality within its borders. It also has the highest number and density of air quality monitoring stations, with over 20 stations equipped to monitor major pollutants.

#### Major Municipalities

The top five most populous cities/towns in the Lower Fraser Valley are:

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
library(dplyr)
library(kableExtra)
df_cities <- readr::read_csv('https://raw.githubusercontent.com/bcgov/air-zone-reports/master/data/out/cities.csv')

tbl_cities <- df_cities %>%
  filter(airzone == 'Lower Fraser Valley')  %>%
  select(Name,C1_COUNT_TOTAL) %>%
   mutate(C1_COUNT_TOTAL = format(C1_COUNT_TOTAL,big.mark = ',')) %>%
  rename(Municipality = Name, `Population (2021)` = C1_COUNT_TOTAL) %>%
  arrange(desc(`Population (2021)`)) %>%
  ungroup() %>%
  dplyr::slice_head(n=5)

nrow(tbl_cities)
```
```{r, echo = FALSE}

kable(tbl_cities)%>%
 kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
