## Northwest Air Zone

The Northwest air zone is one of the seven broad air zones in British Columbia. It is located in the northwest region of the province, bordering Alaska to the west and Yukon to the north. Due to its sparse population, the Northwest air zone does not have air quality monitoring stations that can provide data for this report. 

#### Major Municipalities

The top five most populous cities/towns in the Northwest Air Zone are:


```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
library(dplyr)
library(kableExtra)
df_cities <- readr::read_csv('https://raw.githubusercontent.com/bcgov/air-zone-reports/master/data/out/cities.csv')

tbl_cities <- df_cities %>%
  filter(airzone == 'Northwest')  %>%
  select(Name,C1_COUNT_TOTAL) %>%
  mutate(C1_COUNT_TOTAL = format(C1_COUNT_TOTAL,big.mark = ',')) %>%
  rename(Municipality = Name, `Population (2021)` = C1_COUNT_TOTAL) %>%
  arrange(desc(`Population (2021)`)) %>%
  ungroup() %>%
  dplyr::slice_head(n=5)

nrow(tbl_cities)
```

```{r, echo = FALSE}

 kable(tbl_cities)%>%
 kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  
```
