## Northwest Air Zone

The Northwest Air Zone is one of seven broad air zones across B.C. It is located in the northwest region of the province bordering Alaska to the east and Yukon to the north. Because the northwest air zone is sparsely population, there are no air quality monitoring stations used to report for the Air Quality Management System (AQMS).

#### Major Municipalities

The top five most populous cities/towns in the Northwest Air Zone are:


```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
library(dplyr)
library(kableExtra)
df_cities <- readr::read_csv('https://raw.githubusercontent.com/bcgov/air-zone-reports/master/data/out/cities.csv')

tbl_cities <- df_cities %>%
  filter(airzone == 'Northwest')  %>%
  select(Name,C1_COUNT_TOTAL) %>%
  mutate(C1_COUNT_TOTAL = format(C1_COUNT_TOTAL,big.mark = ',')) %>%
  rename(Municipality = Name, `Population (2021)` = C1_COUNT_TOTAL) %>%
  arrange(desc(`Population (2021)`)) %>%
  ungroup() %>%
  dplyr::slice_head(n=5)

nrow(tbl_cities)
```

```{r, echo = FALSE}

 kable(tbl_cities)%>%
 kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  
```
