## Southern Interior Air Zone

The Southern Interior air zone is one of the seven broad air zones in British Columbia. Situated in the southeastern part of the province, it spans across parts of the Thompson-Okanagan Region, and the Kootenay-Boundary Region. It stretches across broad areas of southern B.C. from the Coast Mountains to the Alberta border. The Southern Interior air zone includes major population centres such as Kamloops, Kelowna, Vernon, Penticton, and Cranbrook.

#### Major Municipalities

The top five most populous cities/towns in the Southern Interior Air Zone are:

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
library(dplyr)
library(kableExtra)
df_cities <- readr::read_csv('https://raw.githubusercontent.com/bcgov/air-zone-reports/master/data/out/cities.csv')

tbl_cities <- df_cities %>%
  filter(airzone == 'Southern Interior')  %>%
  select(Name,C1_COUNT_TOTAL) %>%
  mutate(C1_COUNT_TOTAL = format(C1_COUNT_TOTAL,big.mark = ',')) %>%
  rename(Municipality = Name, `Population (2021)` = C1_COUNT_TOTAL) %>%
  arrange(desc(`Population (2021)`)) %>%
  ungroup() %>%
  dplyr::slice_head(n=5)

nrow(tbl_cities)
```
```{r, echo = FALSE}

 kable(tbl_cities)%>%
 kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  
```
